From Object Classification to Naming: Modeling Entry-level Names for Real-world Objects

### 2019-12-09 papers/ACL2020/experiments.tex

\paragraph{Data}
\gbt{I moved this here cause I think it will be useful to define the different vocabularies here and then be able to simply refer to them later. Btw, consider using `MN-Entry' instead of `MN442'? but maybe having the number in the name is useful to be able to compare.}
\cs{todo after Section~\ref{sect:mn_overview} has been written.}
\begin{itemize}
	\item Test data: overlap of \mn and \vg test data (CITE)
	\item Target vocabulary of test data: overlap of MN442 and VG (\cs{XX} names)
	\item Source of label: \mn, but we compare against \vg
\end{itemize}

>>>>

\paragraph{Data}
We split \mn into training ($21K$~objects) and test data ($1,072$). 
The test data corresponds to the overlap of \mn (MN) and the VG (VG) test split used by  \newcite{anderson2018updown}. 
The target vocabulary of the test data is MN442. %the overlap of MN442 and VG ($355$ names). 
For training using transfer learning, we train on the ground truth labels provided by \mn, but compare to training on \vg labels.
